Spin canonical divisors of log stacky curves

### 2015-06-23 stacky_write_up/spin_cring.tex

In the case of a smooth genus 1 curve, $X$, we know $K_X = 0$, and therefore the only possibilities for half canonical divisors are $\halfcan' = 0$ or $\halfcan' = P-Q$ where $P,Q$ are distinct points, fixed under the hyperelliptic involution. We aim to inductively construct presentations by increasing the values

@@

\begin{example}
\label{eg:g_1_triv}
In the case $\halfcan' = 0,$ it is immediately clear that $R_{\halfcan'} \cong k[x]$ with $x$ a generator in degree 1.
\end{example}

\begin{example}
Let $\sx$ be a stacky curve so that $\halfcan' = P - Q + \frac{1}{3}R_1 + \frac{1}{3}R_2$. Let $u \in H^0(\sx,2\halfcan')$ be any nonzero element, let $x_3 \in H^0(\sx,3\halfcan')$ be an element with a pole at $P$ but not at $Q$ and $y_3 \in H^0(\sx,3\halfcan')$ be an element with a pole at $Q$ but not at $P$. Note that $x_3$ and $y_3$ exist because the linear systems $3P - 3Q + R_1, 3P - 3Q + R_2$ are one dimensional, while the linear system $3P - 3Q \sim P-Q$ is zero dimensional.

Here, we claim $R_{\halfcan'} \cong k[u,x,y_3,y_4]/(xy_3- \alpha uy_4,y_4^2 - \beta x^2 u - \gamma y^2u)$ where $\alpha,\beta,\gamma \in k.$

 and $\deg u = 2, \deg x = \deg y_3 = 3, \deg y_4 = 4,$ where $u,x$ are as in Example ~\ref{eg:g_1_deg_third} and $y_3, y_4$ are as in Proposition ~\ref{prop:sat_two_induction}.

\todo{check admissibility}
\end{example}

>>>>

In the case of a smooth genus 1 curve, $X$, we know $K_X = 0$, and therefore the only possibilities for half canonical divisors are $\halfcan' = 0$ or $\halfcan' = P-Q$ where $P,Q$ are distinct points, fixed under the hyperelliptic involution. We aim to inductively construct presentations by increasing the values of the $e_i$ using Theorem ~\ref{thm:ram_order_ind} and add additional points using Lemma ~\ref{lem:deg1_sat_ind} and Proposition ~\ref{prop:sat_two_induction}

@@

\begin{example}
\label{eg:base-1-0}
In the case $\halfcan' = 0,$ it is immediately clear that $R_{\halfcan'} \cong k[x]$ with $x$ a generator in degree 1.
\end{example}

\begin{example}
\label{eg:base-1-33}
Let $\sx'$ be a stacky curve so that $\halfcan' = P - Q + \frac{1}{3}R_1 + \frac{1}{3}R_2$. In this example, we show
$$R_{\halfcan'} \cong k[u,x_3,y_3,y_4]/(xy_3- \alpha uy_4,y_4^2 - \beta x^2 u - \gamma y^2u)$$
and that $(\sx',\{3,3\})$ is admissible.

Let $u \in H^0(\sx,2\halfcan')$ be any nonzero element, let $x_3 \in H^0(\sx,3\halfcan')$ be an element with a pole at $P$ but not at $Q$ and $y_3 \in H^0(\sx,3\halfcan')$ be an element with a pole at $Q$ but not at $P$. Let $y_4 \in H^0(\sx,3\halfcan')$ be an element with a pole of order 1 at both $P$ and $Q$. Note that $x_3$ and $y_3$ exist because the linear systems $3P - 3Q + R_1, 3P - 3Q + R_2$ are one dimensional, while the linear system $3P - 3Q \sim P-Q$ is zero dimensional.

Then, there exist constants $\alpha,\beta,\gamma \in k$ so that 
$R_{\halfcan'} \cong k[u,x,y_3,y_4]/(xy_3- \alpha uy_4,y_4^2 - \beta x^2 u - \gamma y^2u).$ The proof of this is fairly algorithmic, and analogous to that completed in Example ~\ref{ex:base-377}.

We next check $(\sx',\{3,3\})$ is admissible. We clearly have two generators $x_3,y_3$ in degree 3 with a pole of order $\frac{3-1}{2}$ by construction. Hence, (Ad-i) holds. We next check (Ad-ii) for the point $R_1$, as the case of $R_2$ is symmetric. Here, by construction
$$
\frac{-\ord_{R_1}(z)}{\ord(z)} = \begin{cases}
	0 &\text{ if }z \in \{u,y_3\}\\
	\frac{1}{4} &\text{ if }z = y_4
\end{cases}.$$
Since $0 < \frac{1}{4} < \frac{1}{3}$, (Ad-ii) holds.
Finally, to check (Ad-iii) note that $\max_{d \geq 0}S_{\sigma,J}(i,d) = 0.$ Therefore, $\deg \lfloor 5L \rfloor  = 2 > 1 = 2 \cdot 1 -1 + 0$.
\end{example}

\ssec{Genus 1 Exceptional Cases}
